Multiscale Understanding the Wettability of Doped Two-Dimensional Materials

### 2017-07-22 writing/paper-Tian-gr-wetting.tex
clean up data files

% Created 2017-06-01 Thu 19:09
% Intended LaTeX compiler: pdflatex
\documentclass[journal=jacsat,manuscript=article,email=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\keywords{Two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, eletrical double layer}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy & Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\date{}
\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
\begin{document}

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials interfaces enables new technological opportunities 
  in functional surfaces and molecular epitaxy. Quantifying the interplay between the interfacial forces and electric 
  potential of 2D materials represents the crucial first step for understanding their wettability.
  Here we develop the first theoretical framework to model the wettability of the doped 2D 
  materials by properly bridging the multiscale physical phenomena at the 2D interfaces,
  including: (i) the change of 2D materials surface energy (atomistic scale), 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  (molecular scale), and (iii) the electrical double layer (EDL) formed in the liquid phase (macroscopic scale). 
  The latter two effects are found to be the major mechanisms responsible for the contact angle change upon doping.
  When the doping level is electrostatically tuned, we demonstrate that 2D materials with high quantum capacitances 
  (e.g., transition metal dichalcogenides, TMDCs) possess a wider range of tunability in the interfacial tension. 
  Furthermore, practical considerations such as defect and airborne contamination are also quantitatively discussed. 
  Our analysis implies that the doping level can be another variable to modulate the wettability at the interface of 2D materials,
  as well as the molecular packing behavior on a 2D material-coated surface, 
  essentially faciliating the interfacial engineering of 2D materials.
\end{abstract}
# \maketitle

@@

\section{Introduction}
\label{sec:org435dbee}

Two-dimensional (2D) materials, the crystalline films with a thickness
of one atom or one molecule, combine optical transparency and the
quantum-confined properties
\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress in the scalable production of large-area 2D
materials \cite{Boott_2015,Li_2016} has paved the way for the
applications of functional surfaces and ultrathin membranes
\cite{Prasai_2012,Feng_2016,Rafiee_2010,Yin_2014,Surwade_2015,Hern_ndez_2013}.
The concept of van der Waals (vdW) epitaxy has been further extended
to grow molecular heterostructures on 2D material-coated surfaces for
a variety of applications
\cite{Shi_2012_epitaxy_graphene,Kim_2017_remote_epitaxy,Novoselov_2016}. The
realization of these technologies essentially requires precise control
over the molecular interactions at 2D material interfaces, which
motivates fundamental research of their interfacial properties, in
particular the wettability.  An accurate determination of the
interfacial tension, nevertheless, remains highly disputed
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
literature on understanding the surface science of 2D materials has
highlighted the effects of the airborne contaminants
\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
and the underlying substrate
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
since the length scale for the van der Waals (vdW) radius is
comparable to the thickness of a monolayer. On the other hand, a
subtle but important fact is that the 2D semimetals (e.g, graphene and
silicene) and 2D semiconductors (e.g., transition metal
dichalcogenides (TMDCs)) possess low density of states (DOSs) around
the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
doping, either induced by the surroundings
\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
gating \cite{Das_2008,Perera_2013}, also comes into play. Recent advance
in the \textit{ab initio} calculations and scanning tunneling
microscopy (STM) studies on the adsorbed molecules on graphene
\cite{Muruganathan_2015,Huttmann_2015} has provided some clues to the
doping-dependent vdW interactions. Subsequently, the doping-induced
change in the wettability of graphene has been observed in the
contact-angle experiments
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the molecular dynamics (MD) simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. In
this respect, however, most reports described the doping-dependent
wettability with the basic Young-Lippmann equation (YLE)
\cite{Lippmann_1875}, whereas the interplay between the orientation of
liquid molecules at the interface \cite{Shen_2006} and the electronic
structure of the 2D materials is often ignored. In order to address
the discrepancies among the literature, a general and complete
theoretical picture that bridges the gap between different length
scales, is clearly required.

In this report, we propose the first theoretical framework to model
the change of interfacial tension between liquid and a sheet of
monolayer 2D material. Multiscale physical phenomena are
considered. At the atomistic scale, we formulate the dependence of
surface energy of a 2D material on the doping density using the
quantum capacitance (QC) calculated by the density functional theory
(DFT). Next, the surface-charge-induced reorientation of liquid
molecules adjacent to the interface is associated with an N-body
system, which is resolved by molecular dynamics (MD) simulations,
allowing quantification of the interfacial tension in the absence of
electrolytes in liquid. The effect of the electrical double layer
(EDL) induced by the electrostatic interactions between the 2D
material surface charges and the ionic species in liquid, is then
addressed at the continuum level. Practical considerations, such as
the defect density and the surface contamination are also taken into
account to provide a comprehensive understanding of the
phenomena. Finally, we examine and validate our theory by comparing
with the contact angle changes reported in the electrowetting and the
substrate-induced doping experiments.

\section{Results and Discussions}
\label{sec:org66b0b42}

\subsection{Surface Energy of Doped 2D Materials}
\label{sec:org87cc68c}

@@

First, we model the dependence of \(\gamma_{\mathrm{2D}}\) on the doping
level. Consider a closed system with constant pressure and volume
containing a sheet of free-standing 2D material, following the Euler
homogeneous function theorem of thermodynamics, the total internal
energy of the system \(U\), is given by \(U = TS + \mu_{\mathrm{2D}} N +
\gamma_{\mathrm{2D}} A + \psi_{\mathrm{2D}} q\)
\cite{bard_electrochemical_1980}, where \(T\) is the temperature, \(S\) is
the entropy, \(\mu_{\mathrm{2D}}\) is the chemical potential of the 2D
material per unit lattice, \(N\) is the number of unit lattices, \(A\) is
the area of the 2D material, and \(\psi_{\mathrm{2D}}\) and \(q\) are the
electric potential and total charge in the 2D material,
respectively. At constant \(T\), combining with the first law of
thermodynamics and the differential form of \(U\), it follows:
\begin{equation}
\label{eqn-dgamma-dpsi}
\mathrm{d} \gamma_{\mathrm{2D}} = -\frac{q}{A} \mathrm{d} \psi_{\mathrm{2D}}
                                = -\sigma_{\mathrm{2D}} \mathrm{d} \psi_{\mathrm{2D}}
\end{equation}
relating the surface tension change of a free-standing 2D material as
a function of its doping density \(\sigma_{\mathrm{2D}}\). After bringing an amount of charge
\(q\) from infinity to a charge-neutral 2D material in the
aforementioned system, the surface energy change is therefore given
by:
\begin{equation}
\label{eqn-delta-gamma-sigma-free-2D}
\Delta \gamma_{\mathrm{2D}} = - \int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{2D}} \mathrm{d}\psi'
                            = - \int_{0}^{\sigma_{\mathrm{2D}}} \sigma' \left( \frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d} \sigma'
\end{equation}
where \(C_{\mathrm{2D}} = g(E_{\mathrm{F}}) e^{2}\) is the quantum
capacitance of the 2D material \cite{davies_two-dimensional_1997,Das_Sarma_2011},
\(g(E_{\mathrm{F}})\) is the DOS as a function of \(E_{\mathrm{F}}\),
\(\psi_{\mathrm{2D}} = -(E_{\mathrm{F}} - E_{\mathrm{F,0}})/e\) and
\(E_{\mathrm{F,0}}\) corresponds to the Fermi level of the 2D material
at the charge neutral point (CNP). Accordingly, eq
\ref{eqn-delta-gamma-sigma-free-2D} provides a simple relation which
depicts the surface tension change of a 2D material at the
quantum-mechanical level. We have calculated the DOSs as a function of
\(E_{\mathrm{F}}\) for a variety of 2D materials using the density
functional theory \cite{tian_multiscale_2016}. Note that we take into
account a fractional component of the exact exchange from the
Hartree-Fock (HF) theory hybridized with the DFT exchange-correlation
functional at the level of the HSE06 hybrid functional. Therefore, any
limitation of the exchange and correlation functional utilized in the
chemical description of the energy levels can be improved. The
following 2D materials are considered: TMDC monolayers (MX\(_{\text{2}}\), M =
Mo, W and X = S, Se, Te), silicene, germanene, phosphorene (monolayer
black phosphorus), and graphene. The doping density in a 2D material
is calculated by integrating the DOS from its intrinsic Fermi level,
i.e., \(\sigma_{\mathrm{2D}} = \int_{E_{\mathrm{F,0}}}^{E_{\mathrm{F}}}
g(E')e \mathrm{d}E'\) \cite{john_quantum_2004}.

@@

\subsection{Reorientation of Liquid Molecules}
\label{sec:org188528c}

@@

\begin{equation}
\label{eqn-delta-gamma-decompose}
\Delta \gamma_{\mathrm{2D-L}} = \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}
                              + \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}
\end{equation}
where \(\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}\) and \(\Delta
\gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}\) correspond to the contributions
from the reorientation and the EDL effects, respectively, as
schematically illustrated in Figure \ref{fig:scheme-method}. We also
assume that \(\Delta \gamma_{\mathrm{2D-L}}^{Orien}\) is independent of
the electrolyte concentration, since the concentration of liquid
molecules is typically orders-of-magnitude higher.

First we discuss the orientation effect. Understanding the
reorientation effect involves positioning and sampling the collective,
time-averaged motion of liquid molecules near the interface, which is
a standard molecular dynamics (MD) problem. Note that even with the
state-of-the-art MD algorithms, it remains challenging to accommodate
the calculations for the EDL, in which the length scale of electric
field can be larger than one micrometer in diluted electrolyte
solutions, e.g., pure water with self-ionized H\(_{\text{3}}\)O\(^{\text{+}}\) and OH\(^{\text{-}}\)
ions. Here we consider the graphene-water interface as a model
system. All MD simulations were carried out using the GROMACS 4.5
software package \cite{Hess_2008}. Monolayer graphene was modeled as an
infinite rigid sheet in the x-y plane. The carbon atoms of graphene
were treated as uncharged Lennard-Jones (LJ) spheres with \(\sigma\) =
0.34 nm and \(\epsilon\) = 0.223 kJ/mol \cite{Cheng_1990}, using the
force-field parameters reported by Tummala and Striolo
\cite{Tummala_2008}. The doping effect is included by assigning an equal
amount of charge \(\sigma_{\mathrm{2D}} / \rho_{\mathrm{G}}\), where
\(\rho_{\mathrm{G}}\) is the surface density of carbon atoms, to each
carbon atom. The \(\sigma_{\mathrm{2D}}\) range considered here
approximately correspond to the partial atomic charge from −0.012 to
0.012 \(e/\mathrm{atom}\). Water molecules were modeled using the SPC/E
model \cite{Berendsen_1987} with bond lengths and angles of water
molecules constrained using the SETTLE algorithm
\cite{Miyamoto_1992}. Lennard-Jones interactions were treated with a
cutoff distance of 1 nm, with those between different atoms calculated
using the standard geometric averaging rule. Long-range electrostatic
interactions were treated using the particle mesh Ewald (PME)
summation method \cite{Darden_1993,Essmann_1995} with a short-range
cutoff distance of 1 nm. The velocity-rescaled Berendsen thermostat
was implemented to maintain a constant system temperature of 298.15 K
\cite{Bussi_2007}. All simulations were carried out under the NVT
ensemble.

In order to precisely determine the interfacial interactions using MD
simulations, instead of the commonly used model that compared the
nanoscale contact angle by placing a nanodroplet onto a sheet of
suspended 2D material
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
we simulate the difference of the total potential energy, \(E\), between
two separate systems that contain (i) only water molecules with two
surfaces exposing to vacuum (L), and (ii) the same amount of water
molecules with one surface in contact with graphene (placed at z = 0)
and the other surface exposing to vacuum (GL) (see Figure
\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)) . Periodic boundary
conditions are used in all three directions of the simulation boxes in
both systems. Additionally, a vacuum layer of 3 nm thick along the
\emph{z}-axis is placed to separate the periodic images of the
graphene-water system. The total energy in both systems can be
formulated as: \(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
2\gamma_{\mathrm{L}}S\) and
\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}} +
\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively, where
\(\mu_{\mathrm{L}}\) is the chemical potential per water molecule in the
bulk phase, \(n_{\mathrm{L}}\) is the number of liquid molecules in the
simulation box, and \(S\) is the area of the \emph{xy}-plane.  A simulation
box with a sufficiently large length of 21 nm in the \emph{z}-direction is used,
with a 18-nm thick block of water molecules, to minimize the effect of
the long-range electrostatic interaction between the charged graphene
and the water molecules at the water-vacuum interface, by ensuring
that the time-averaged dipole moment for the water molecules at the
water-vacuum interface is approximately zero (see Supporting Information
Figure S1).  One can show that \(E_{\mathrm{GL}} - E_{\mathrm{L}} =
(\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}} - \gamma_{L})S =
(\Phi + 2 \gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial
energy, which is defined as \(\Phi = \gamma_{\mathrm{2D-L}} -
\gamma_{\mathrm{2D}} - \gamma_{\mathrm{L}}\), and combining with eq
\ref{eqn-def-Young-Delta-theta}, the change of interfacial energy
\(\Delta \Phi\) can be formulated as:
\begin{equation}
\label{eqn-Delta-Phi-Delta-cos}
\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S - 2\Delta \gamma_{\mathrm{2D}} = -\gamma_{\mathrm{L}} (\Delta \cos \theta)^{\mathrm{Orien}}
\end{equation}
where \((\Delta\cos \theta)^{\mathrm{Orien}}\) corresponds to the
contact angle change due to the reorientation effect. Note that in the
current MD simulation setup, the surface tension of the 2D material
remains unchanged (i.e. \(\Delta \gamma_{\mathrm{2D}}=0\)), since the
Fermi level change with
respect to \(\sigma_{\mathrm{2D}}\) (see eq
\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm. In all simulations we assume a
constant surface tension of water \(\gamma_{\mathrm{L}}=72.8\
\mathrm{mJ}\cdot \mathrm{m}^{-2}\). Accordingly, \(\Delta \Phi\) follows
\(\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S = \Delta
\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where \(\Delta
\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) correspond to
the change for the vdW and Coulombic interaction potentials,
respectively.

>>>>

% Created 2017-07-22 Sat 15:09
% Intended LaTeX compiler: pdflatex
\documentclass[journal=jacsat,manuscript=article,email=true,hyperref=true,keywords=true]{achemso}
 \usepackage{minted}
 \usepackage{graphicx}
\usepackage{float}
\usepackage{xcolor}
\usepackage{amsmath}
\usepackage{fontspec}
\author{Tian Tian}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\author{Siyu Li}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Lingling Zhao}
\affiliation{Key Laboratory of Energy Thermal Conversion and Control of Ministry of Education, School of Energy and Environment, Southeast University, Nanjing, Jiangsu 210096, China}
\author{Elton J. G. Santos}
\affiliation{School of Mathematics and Physics, Queen's University Belfast, United Kingdom}
\affiliation{School of Chemistry and Chemical Engineering, Queen's University Belfast, United Kingdom}
\author{Shangchao Lin}
\email{slin@eng.fsu.edu.}
\affiliation{Department of Mechanical Engineering, Materials Science and Engineering Program, FAMU-FSU College of Engineering, Florida State University, Tallahassee, Florida 32310, United States}
\author{Chih-Jen Shih}
\email{chih-jen.shih@chem.ethz.ch}
\affiliation{Institute for Chemical and Bioengineering, ETH Z{\"{u}}rich,  Vladimir Prelog Weg 1, CH-8093 Z{\"{u}}rich, Switzerland}
\keywords{two-dimensional materials, doping, wettability, multiscale analysis, MD Simulation, electrical double layer}
\date{}
\title{Multiscale Understanding the Wettability of Doped Two-Dimensional Materials}
\begin{document}

\begin{tocentry}
\includegraphics[width=9cm]{../img/TOC.pdf}
\end{tocentry}

\newpage{}
\begin{abstract}
  Engineering molecular interactions at two-dimensional (2D) materials interfaces enables new technological opportunities 
  in functional surfaces and molecular epitaxy. Quantifying the interplay between the interfacial forces and electric 
  potential of 2D materials represents the crucial first step for understanding their wettability.
  Here we develop the first theoretical framework to model the wettability of the doped 2D 
  materials by properly bridging the multiscale physical phenomena at the 2D interfaces,
  including: (i) the change of 2D materials surface energy (atomistic scale), 
  (ii) the molecular reorientation of liquid molecules adjacent to the interface, 
  (molecular scale), and (iii) the electrical double layer (EDL) formed in the liquid phase (macroscopic scale). 
  The latter two effects are found to be the major mechanisms responsible for the contact angle change upon doping.
  When the doping level is electrostatically tuned, we demonstrate that 2D materials with high quantum capacitances 
  (e.g., transition metal dichalcogenides, TMDCs) possess a wider range of tunability in the interfacial tension. 
  Furthermore, practical considerations such as defect and airborne contamination are also quantitatively discussed. 
  Our analysis implies that the doping level can be another variable to modulate the wettability at the interface of 2D materials,
  as well as the molecular packing behavior on a 2D material-coated surface, 
  essentially facilitating the interfacial engineering of 2D materials.
\end{abstract}
% \textbf{Keywords}
% two-dimensional materials, doping, wettability, multiscale analysis, molecular dynamics simulation, electrical double layer
 \maketitle

@@

\section{Introduction}
\label{sec:org828e535}

Two-dimensional (2D) materials, the crystalline films with a thickness
of one atom or one molecule, combine optical transparency and the
quantum-confined properties
\cite{Novoselov_2005,Mas_Ballest__2011,Novoselov_2016}.  Recent progress
in the scalable production of large-area 2D materials
\cite{Boott_2015,Li_2016} has paved the way for the applications of
functional surfaces and ultrathin membranes
\cite{Prasai_2012,Feng_2016,Rafiee_2010,Yin_2014,Surwade_2015,Hern_ndez_2013}.
The concept of van der Waals (vdW) epitaxy has been further extended
to grow molecular heterostructures on 2D material-coated surfaces for
a variety of applications
\cite{Shi_2012_epitaxy_graphene,Kim_2017_remote_epitaxy,Novoselov_2016}. The
realization of these technologies essentially requires precise control
over the molecular interactions at 2D material interfaces, which
motivates fundamental research of their interfacial properties, in
particular the wettability.  An accurate determination of the
interfacial tension, nevertheless, remains highly disputed
\cite{taherian2013what,Kozbial_2015,Parobek_2015,Govind_Rajan_2016}. Early
literature on understanding the surface science of 2D materials has
highlighted the effects of the airborne contaminants
\cite{li_effect_2013,Xu_2013_withwhat,kozbial_study_2014,Kozbial_2015,Chow_2015}
and the underlying substrate
\cite{raj_wettability_2013,rafiee_wetting_2012,shih_breakdown_2012,shih_wetting_2013},
since the length scale for the van der Waals (vdW) radius is
comparable to the thickness of a monolayer. On the other hand, a
subtle but important fact is that the 2D semimetals (e.g, graphene and
silicene) and 2D semiconductors (e.g., transition metal
dichalcogenides (TMDCs)) possess low density of states (DOS) around
the intrinsic Fermi level (\(E_{\mathrm{F}}\)), such that the effect of
doping, either induced by the surroundings
\cite{Chen_2013,Varchon_2007,Giovannetti_2008}, or by the electrostatic
gating \cite{Das_2008,Perera_2013}, also comes into play. Recent advance
in the \textit{ab initio} calculations and scanning tunneling
microscopy (STM) studies on the adsorbed molecules on graphene
\cite{Muruganathan_2015,Huttmann_2015} has provided some clues to the
doping-dependent vdW interactions. Subsequently, the doping-induced
change in the wettability of graphene has been observed in the
contact-angle experiments
\cite{hong_mechanism_2016,goniszewski_correlation_2016,ashraf_doping-induced_2016},
and the molecular dynamics (MD) simulations
\cite{ostrowski_tunable_2014,ren_interfacial_2015,Taherian_2015,daub_electrowetting_2007}. In
this respect, however, most reports described the doping-dependent
wettability with the basic Young-Lippmann equation (YLE)
\cite{Lippmann_1875}, whereas the interplay between the orientation of
liquid molecules at the interface \cite{Shen_2006} and the electronic
structure of the 2D materials is often ignored. In order to address
the discrepancies among the literature, a general and complete
theoretical picture that bridges the gap between different length
scales, is clearly required.

In this report, we propose the first theoretical framework to model
the change of interfacial tension between liquid and a sheet of
monolayer 2D material. Multiscale physical phenomena are considered,
as shown in Figure \ref{fig:scheme-method}. At the atomistic scale, we
formulate the dependence of surface energy of a 2D material on the
doping density using the quantum capacitance (QC) calculated by the
density functional theory (DFT). Next, the surface-charge-induced
reorientation of liquid molecules adjacent to the interface is
associated with an N-body system, which is resolved by molecular
dynamics (MD) simulations, allowing quantification of the interfacial
tension in the absence of electrolytes in liquid. The effect of the
electrical double layer (EDL) induced by the electrostatic
interactions between the 2D material surface charges and the ionic
species in liquid, is then addressed at the continuum level. Practical
considerations, such as the defect density and the surface
contamination are also taken into account to provide a comprehensive
understanding of the phenomena. Finally, we examine and validate our
theory by comparing with the contact angle changes reported in the
electrowetting and the substrate-induced doping experiments.

\section{Results and Discussions}
\label{sec:orgc095477}

\subsection{Surface Energy of Doped 2D Materials}
\label{sec:org28f87f6}

@@

First, we model the dependence of \(\gamma_{\mathrm{2D}}\) on the doping
level. Consider a closed system with constant pressure and volume
containing a sheet of free-standing 2D material, following the Euler
homogeneous function theorem of thermodynamics, the total internal
energy of the system \(U\), is given by \(U = TS + \mu_{\mathrm{2D}} N +
\gamma_{\mathrm{2D}} A + \psi_{\mathrm{2D}} q\)
\cite{bard_electrochemical_1980}, where \(T\) is the temperature, \(S\) is
the entropy, \(\mu_{\mathrm{2D}}\) is the chemical potential of the 2D
material per unit lattice, \(N\) is the number of unit lattices, \(A\) is
the area of the 2D material, and \(\psi_{\mathrm{2D}}\) and \(q\) are the
electric potential and total charge in the 2D material,
respectively. At constant \(T\), combining with the first law of
thermodynamics and the differential form of \(U\), it follows:
\begin{equation}
\label{eqn-dgamma-dpsi}
\mathrm{d} \gamma_{\mathrm{2D}} = -\frac{q}{A} \mathrm{d} \psi_{\mathrm{2D}}
                                = -\sigma_{\mathrm{2D}} \mathrm{d} \psi_{\mathrm{2D}}
\end{equation}
relating the surface tension change of a free-standing 2D material as
a function of its doping density \(\sigma_{\mathrm{2D}}\). After bringing an amount of charge
\(q\) from infinity to a charge-neutral 2D material in the
aforementioned system, the surface energy change is therefore given
by:
\begin{equation}
\label{eqn-delta-gamma-sigma-free-2D}
\Delta \gamma_{\mathrm{2D}} = - \int_{0}^{\psi_{\mathrm{2D}}} \sigma_{\mathrm{2D}} \mathrm{d}\psi'
                            = - \int_{0}^{\sigma_{\mathrm{2D}}} \sigma' \left( \frac{1}{C_{\mathrm{2D}}}\right) \mathrm{d} \sigma'
\end{equation}
where \(C_{\mathrm{2D}} = g(E_{\mathrm{F}}) e^{2}\) is the quantum
capacitance of the 2D material \cite{davies_two-dimensional_1997,Das_Sarma_2011},
\(g(E_{\mathrm{F}})\) is the DOS as a function of \(E_{\mathrm{F}}\),
\(\psi_{\mathrm{2D}} = -(E_{\mathrm{F}} - E_{\mathrm{F,0}})/e\) and
\(E_{\mathrm{F,0}}\) corresponds to the Fermi level of the 2D material
at the charge neutral point (CNP). Accordingly, eq
\ref{eqn-delta-gamma-sigma-free-2D} provides a simple relation which
depicts the surface tension change of a 2D material at the
quantum-mechanical level. We have calculated the DOS as a function of
\(E_{\mathrm{F}}\) for a variety of 2D materials using the density
functional theory \cite{tian_multiscale_2016}. Note that we take into
account a fractional component of the exact exchange from the
Hartree-Fock (HF) theory hybridized with the DFT exchange-correlation
functional at the level of the HSE06 hybrid functional. Therefore, any
limitation of the exchange and correlation functional utilized in the
chemical description of the energy levels can be improved. The
following 2D materials are considered: TMDC monolayers (MX\(_{\text{2}}\), M =
Mo, W and X = S, Se, Te), silicene, germanene, phosphorene (monolayer
black phosphorus), and graphene. The doping density in a 2D material
is calculated by integrating the DOS from its intrinsic Fermi level,
i.e., \(\sigma_{\mathrm{2D}} = \int_{E_{\mathrm{F,0}}}^{E_{\mathrm{F}}}
g(E')e \mathrm{d}E'\) \cite{john_quantum_2004}.

@@

\subsection{Reorientation of Liquid Molecules}
\label{sec:org8d3c56f}

@@

\begin{equation}
\label{eqn-delta-gamma-decompose}
\Delta \gamma_{\mathrm{2D-L}} = \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}
                              + \Delta \gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}
\end{equation}
where \(\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}\) and \(\Delta
\gamma_{\mathrm{2D-L}}^{\mathrm{EDL}}\) correspond to the contributions
from the reorientation and the EDL effects, respectively. We also
assume that \(\Delta \gamma_{\mathrm{2D-L}}^{\mathrm{Orien}}\) is independent of
the electrolyte concentration, since the concentration of liquid
molecules is typically orders-of-magnitude higher.

First we discuss the orientation effect. Understanding the
reorientation effect involves positioning and sampling the collective,
time-averaged motion of liquid molecules near the interface, which is
a standard molecular dynamics (MD) problem. Note that even with the
state-of-the-art MD algorithms, it remains challenging to accommodate
the calculations for the EDL, in which the length scale of electric
field can be larger than one micrometer in diluted electrolyte
solutions, e.g., pure water with self-ionized H\(_{\text{3}}\)O\(^{\text{+}}\) and OH\(^{\text{-}}\)
ions. Here we consider the graphene-water interface as a model
system. All MD simulations were carried out using the GROMACS 4.5
software package \cite{Hess_2008}. Monolayer graphene was modeled as an
infinite rigid sheet in the x-y plane. The carbon atoms of graphene
were treated as uncharged Lennard-Jones (LJ) spheres with \(\sigma\) =
0.34 nm and \(\epsilon\) = 0.223 kJ/mol \cite{Cheng_1990}, using the
force-field parameters reported by Tummala and Striolo
\cite{Tummala_2008}. The doping effect is included by assigning an equal
amount of charge \(\sigma_{\mathrm{2D}} / \rho_{\mathrm{G}}\), where
\(\rho_{\mathrm{G}}\) is the surface density of carbon atoms, to each
carbon atom. The \(\sigma_{\mathrm{2D}}\) range considered here
approximately correspond to the partial atomic charge from −0.012 to
0.012 \(e/\mathrm{atom}\). Water molecules were modeled using the SPC/E
model \cite{Berendsen_1987} with bond lengths and angles of water
molecules constrained using the SETTLE algorithm
\cite{Miyamoto_1992}. Lennard-Jones interactions were treated with a
cutoff distance of 1 nm, with those between different atoms calculated
using the standard geometric averaging rule. Long-range electrostatic
interactions were treated using the particle mesh Ewald (PME)
summation method \cite{Darden_1993,Essmann_1995} with a short-range
cutoff distance of 1 nm. The velocity-rescaled Berendsen thermostat
was implemented to maintain a constant system temperature of 298.15 K
\cite{Bussi_2007}. All simulations were carried out under the NVT
ensemble, and the equations of motion of water molecules were
integrated over a range of 20 ns with 10\(^{\text{7}}\) steps.

In order to precisely determine the interfacial interactions using MD
simulations, instead of the commonly used model that compared the
nanoscale contact angle by placing a nanodroplet onto a sheet of
suspended 2D material
\cite{ostrowski_tunable_2014,daub_electrowetting_2007,ren_interfacial_2015,Taherian_2015},
we simulate the difference of the total potential energy, \(E\), between
two separate systems that contain (i) only water molecules with two
surfaces exposing to vacuum (L), and (ii) the same amount of water
molecules with one surface in contact with graphene (placed at z = 0)
and the other surface exposing to vacuum (GL) (see Figure
\ref{fig:MD-res}(a) and \ref{fig:MD-res}(b)). Periodic boundary
conditions are used in all three directions of the simulation boxes in
both systems. Additionally, a vacuum layer of 3 nm thick along the
\emph{z}-axis is placed to separate the periodic images of the
graphene-water system. The total energy in both systems can be
formulated as: \(E_{\mathrm{L}} = \mu_{\mathrm{L}}n_{\mathrm{L}} +
2\gamma_{\mathrm{L}}S\) and
\(E_{\mathrm{GL}}=\mu_{\mathrm{L}}n_{\mathrm{L}}+(\gamma_{\mathrm{L}} +
\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}})S\), respectively, where
\(\mu_{\mathrm{L}}\) is the chemical potential per water molecule in the
bulk phase, \(n_{\mathrm{L}}\) is the number of liquid molecules in the
simulation box, and \(S\) is the area of the \emph{xy}-plane.  A simulation
box with a sufficiently large length of 21 nm in the \emph{z}-direction is used,
with a 18-nm thick block of water molecules, to minimize the effect of
the long-range electrostatic interaction between the charged graphene
and the water molecules at the water-vacuum interface, by ensuring
that the time-averaged dipole moment for the water molecules at the
water-vacuum interface approaches zero (see Supporting Information
Figure S1).  One can show that \(E_{\mathrm{GL}} - E_{\mathrm{L}} =
(\gamma_{\mathrm{2D-L}} + \gamma_{\mathrm{2D}} - \gamma_{L})S =
(\Phi + 2 \gamma_{\mathrm{2D}})S\), where \(\Phi\) is the interfacial
energy, which is defined as \(\Phi = \gamma_{\mathrm{2D-L}} -
\gamma_{\mathrm{2D}} - \gamma_{\mathrm{L}}\), and combining with eq
\ref{eqn-def-Young-Delta-theta}, the change of interfacial energy
\(\Delta \Phi\) can be formulated as:
\begin{equation}
\label{eqn-Delta-Phi-Delta-cos}
\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S - 2\Delta \gamma_{\mathrm{2D}} = -\gamma_{\mathrm{L}} (\Delta \cos \theta)^{\mathrm{Orien}}
\end{equation}
where \((\Delta\cos \theta)^{\mathrm{Orien}}\) corresponds to the
contact angle change due to the reorientation effect. Note that in the
current MD simulation setup, the surface tension of the 2D material
remains unchanged (i.e. \(\Delta \gamma_{\mathrm{2D}}=0\)), since the
Fermi level change with
respect to \(\sigma_{\mathrm{2D}}\) (see eq
\ref{eqn-delta-gamma-sigma-free-2D}) is not included in the algorithm. In all simulations we assume a
constant surface tension of water \(\gamma_{\mathrm{L}}=72.8\
\mathrm{mJ}\cdot \mathrm{m}^{-2}\). Accordingly, \(\Delta \Phi\) follows
\(\Delta \Phi = \Delta (E_{\mathrm{GL}} - E_{\mathrm{L}})/S = \Delta
\Phi_{\mathrm{LJ}} + \Delta \Phi_{\mathrm{Coul}}\), where \(\Delta
\Phi_{\mathrm{LJ}}\) and \(\Delta \Phi_{\mathrm{Coul}}\) correspond to
the change for the vdW and Coulombic interaction potentials,
respectively.
